Program Equivalence : Relational Separation Logic interactive prover implemented in Maude

### 2018-06-19 paper/paper_after_guide.tex
intermediary commit
wrote about actions and program states

Each proof rule in the Separation Logic and Relational Separation Logic has been translated into a Maude rewrite rule. The resulting rules have been marked as non-executable because the goal is to control when they are applied.
\subsection{Interaction by Maude LOOP-MODE}
Maude's LOOP-MODE module is the entry point for any interactive Maude application, being the only way to store state between commands. In this chapter we will discuss how we handle input and output , the structure of a state and the role every element plays in the execution of the prover.\\

We will make a distinction between \textbf{Loop state}, which specific to Maude's LOOP-MODE module and the \textbf{Prover state} which is specific to our use-case, and holds the necessary data related to the state of the proof we are currently working on. The \textbf{Prover state} is encapsulated within \textbf{Loop state}.
\subsection{Input and output handling}
To understand how our prover handles input and output, it is important to note that the flows of the LOOP-MODE module is as follows: 
\begin{figure}
	Aici va veni figura care explica input -> rewriting maxim -> output
\end{figure}
\subsection{State of the program}
Following the examples provided together with the Maude Manual \cite{manual}, our state is composed multiple sections modified accordingly during program execution .
\subsection{Prover execution flow}
In this section we will describe the flow of a demonstration made using our prover.
\subsection{Automated processes}
This section will describe the functional parts of the prover which have been automated to make it more user-friendly and even prove sub-goals of the main demonstration by itself. Since the automation of the prover is part of the future goals of this project, we will also include a few notes on how we might approach problems related to this goal, even though they have not been implemented yet.
\subsubsection{Automatic matching of axioms and previously proven goals}
\subsubsection{Automatic demonstration of implications}
\subsection{User Interface}
Since our project aims to simplify the demonstrations of Separation Logic / Relational Separation Logic formulae, using an interactive prover, the user interface plays a major role in the success of the project - the easier it is to use and understand, the more chances of success it has. This idea has been presented in \cite{primer}, when discussing key elements of tools related to program verification. \\

>>>>

Each proof rule in the Separation Logic and Relational Separation Logic has been translated into a Maude rewrite rule. The resulting rules have been marked as non-executable because the goal is to control when they are applied.
\\
The prover is centered around the concept of \textbf{Goals} which can be one of the three things: 
\begin{itemize}
	\item {Hoare Quadruple} - corresponding to Relational Separation Logic
	\item {Hoare Triple} - corresponding to Separation Logic
	\item {Implication between relations / assertions} 
\end{itemize} 
The proof rules are interpreted in a bottom-up manner, meaning that applying a rule to a goal matching the conclusion of a rule will generate new goals consisting of the hypothesis elements of the rule.
\begin{figure}
	This figure will explain how we translated the proof rules into Maude syntax
\end{figure}
\subsubsection{Sort Hierarchy}
This section will describe the sorts defined in Maude to handle the constructs of both Separation logics.
\subsection{Language Grammar and executable semantics}
This section will describe how we defined our language in Maude [and how it is possible to create executable semantics for this language]
\subsection{Interaction by Maude LOOP-MODE}
Maude's LOOP-MODE module is the entry point for any interactive Maude application, being the only way to store state between commands. In this chapter we will discuss how we handle input and output , the structure of a state and the role every element plays in the execution of the prover.\\

We will make a distinction between \textbf{Loop state}, which specific to Maude's LOOP-MODE module and the \textbf{Prover state} which is specific to our use-case, and holds the necessary data related to the state of the proof we are currently working on. The \textbf{Prover state} is encapsulated within \textbf{Loop state}.
\subsection{Input and output handling}
To understand how our prover handles input and output, it is important to note that the flows of the LOOP-MODE module is as follows: 
\begin{figure}
	Aici va veni figura care explica input -> rewriting maxim -> output
\end{figure}
\subsection{State of the program}
Following the examples provided together with the Maude Manual \cite{manual}, our state is composed multiple sections modified accordingly during program execution .
\begin{itemize}
	\item{\textbf{Action} - represents the current action to be executed by the prover, more details about supported actions are included in the following sections.}
	\item{\textbf{Root Goal} - represents the end-goal of this demonstration}
	\item{\textbf{Current Goal} - the goal being treated currently - all actions will be applied to this goal}
	\item{\textbf{Goal Stack} - Stack of goals necessary to be proven in order to prove the root goal. The current goal is the last element popped from the stack and new elements are generated and pushed by the application of proof rules to the current goal.}
	\item{\textbf{Proven Goals} - List of goals which have been already been proven or axioms. Each goal will be first checked to see if it matches any goal in this list to prevent repeating the same proofs.}
	\item{\textbf{Staging output} - contains the output generated by the current action, before being passed to the Loop state. This staging mechanism enables each action (user or system) to generate output independent of the other actions.}
\end{itemize}
\subsection{Prover execution flow}
In this section we will describe the flow of a demonstration made using our prover.
\subsubsection{User Actions}
User actions are the main entry point for user interaction and they describe how the user intends to process the current goal.
\begin{itemize}
	\item {Rule application action - indicates the application of a specific rule to the current goal, the action can be parameterized or not, depending on the rule.}
	\item {ok action - admits the current goal}
	\item {showGoal action - prints the current goal to the console - it does not modify the state of the prover}
\end{itemize}
\subsubsection{System Actions}
System actions were implemented to mimic the behaviour of a "chain of responsibility" design pattern from object-oriented programming. The system actions are all applied in order before asking for user input. System actions are the main component through which our prover can be enriched with other features in the future, because integrating a new system action is simple. At the moment, the system actions are:
\begin{itemize}
	\item {check} - marks the current goal to be checked against previously proven goals or axioms
	\item {implication} - marks the current goal to be run through the implication prover - in case the goal is an implication, try to prove it automatically
	\item {stop} - when there are no more sub-goals to be proven, the prover should stop and indicate the success of proving the root goal
\end{itemize}
\subsection{Automated processes}
This section will describe the functional parts of the prover which have been automated to make it more user-friendly and even prove sub-goals of the main demonstration by itself. Since the automation of the prover is part of the future goals of this project, we will also include a few notes on how we might approach problems related to this goal, even though they have not been implemented yet.
\subsubsection{Automatic matching of axioms and previously proven goals}
\subsubsection{Automatic demonstration of implications}
\subsection{User Interface}
Since our project aims to simplify the demonstrations of Separation Logic / Relational Separation Logic formulae, using an interactive prover, the user interface plays a major role in the success of the project - the easier it is to use and understand, the more chances of success it has. This idea has been presented in \cite{primer}, when discussing key elements of tools related to program verification. \\
